Case Study/Application

### 2020-01-27 chapters/03_methods.Rmd
work with testing ppcheck function, etc

@@

### This whole section follows Morris et al (probably too) closely right now -- encorporate more from Riebler, Simpson, Besag
We can encode spatial information into Bayesian models in several ways. Conditional Autoregressive (CAR) priors are one of the most widespread Bayesian methods for modeling spatial autocorrelation. Conditional Autoregressive models were introduced in Besag 1974 and remain perhaps the primary method for Bayesian areal data modeling. CAR models are used as $priors$, not as the actual observation model.

@@

Precision matrix $Q$ can be defined for multivariate normal $\phi$ using two other $M$x$M$ matrices: the neighborhood matrix $W$ as well as diagonal matrix $D$ in which $d_{ii}$ indicates the number of neighbors region $i$ has. All off-diagonal entries are 0. Using these matrices, $Q$ is defined

@@

Various graphical checks of priors and posteriors are helpful tools in building, improving, and comparing Bayesian models. The application portion of this honors follows Michael Betancourt's "Towards a Principled Bayesian Workflow" as well as ______ in terms of using visual aids for diagnosing issues with models and comparing quality of fit between models. Only the most "useful" plots are included below, for more on using graphics throughout a Bayesian workflow see Betancourt or Gabry.

>>>>

## Spatial Autocorrelation

@@

### This whole section follows Morris et al (probably too) closely right now -- incorporate more from Riebler, Simpson, Besag

We can encode spatial information into Bayesian models in several ways. Conditional Autoregressive (CAR) priors are one of the most widespread Bayesian methods for modeling spatial autocorrelation. Conditional Autoregressive models were introduced in Besag 1974 and remain perhaps the primary method for Bayesian areal data modeling. CAR models are used as $priors$, not as the actual observation model.

@@

Precision matrix $Q$ can be defined for multivariate normal $\phi$ using two other $N$x$N$ matrices: the neighborhood matrix $W$ as well as diagonal matrix $D$ in which $d_{ii}$ indicates the number of neighbors region $i$ has. All off-diagonal entries are 0. Using these matrices, $Q$ is defined

@@

Various graphical checks of priors and posteriors are helpful tools in building, improving, and comparing Bayesian models. The application portion of this honors follows Michael Betancourt's "Towards a Principled Bayesian Workflow" as well as Gabry et al's "Visualization in a Bayesian Workflow" in terms of using visual aids for diagnosing issues with models and comparing quality of fit between models. Only the most "useful" plots are included below, for more on using graphics throughout a Bayesian workflow see Betancourt or Gabry.

### 2020-01-27 chapters/04_application.Rmd
work with testing ppcheck function, etc

---
title: "Case Study/Application"
author: "Raven McKnight"
date: "1/16/2020"
output:
  pdf_document:
    toc: yes
  html_document:
    theme: paper
    toc: yes
    toc_float: yes
---

@@

# Case Study

## Background

@@

## Data Description

### Metro Transit Data

### Covariates

## Data Preparation

## Modeling

### Model 1: Poisson Regression

@@

### Horseshoe Prior

@@

#### Divergences

@@

#### Variables Selected

@@

### Overdispersion

@@

### Spatial Structure

>>>>

---
title: "Case Study/Application"
author: "Raven McKnight"
output:
  pdf_document:
    number_sections: true
  html_document:
    theme: paper
    toc: yes
    toc_float: yes
---

@@

# Background

@@

# Data Description

## Metro Transit Data

## Covariates

# Data Preparation

# Modeling

## Model 1: Poisson Regression

@@

## Horseshoe Prior

@@

## Divergences

@@

## Variables Selected

@@

## Overdispersion

@@

## Spatial Structure
